---
title: 'Stat 159 Homework 2: Simple Regression Analysis'
author: "Andrew Shibata"
date: "October 7, 2016"
output: html_document
---

```{r, echo=FALSE, message=FALSE}
#Calling package for later use
library(xtable)

```
\section{Abstract}

This report reproduces the Advertising data visualization found in section 3.1 **Simple Linear Regression** of *An Introduction to Statistical Learning*. The concepts addressed in this assignment were using command line Rscripts and file output in R.

\Section{Introduction}

The Advertising data set explores the relationship between advertising budgets for different appliances and the resulting sales. This report conducts simple regression analysis to predict expected sales values as a function of TV advertising budget. 

\section{Data}

Here is the table representing the Advertising data set:
```{r,echo=FALSE,results='asis'}
load('../data/eda-output.txt')
xtable(combined_summary,caption='Summary Statistics for Advertising')
```

\section{Methodology}

\section{Results}

\section{Conclusions}